\documentclass[../main.tex]{subfiles}
\begin{document}

\begin{rmk}
  A scheme will be a 
  ``space modelled on $\M$ with an open cover by affine schemes''.
  Since every ``space'' in $\M\SET$ is modelled on $\M$,
  we first define the notion of open covers for affine schemes,
  then define it for general $X \in \M\SET$.

  We define closed subfunctors of affine schemes first, 
  then define open ones as ``complements'' of closed.
\end{rmk}

\begin{dfn}[Closed Subfunctors of Affine Schemes]

  Let $X \in \AFF$.
  For $I \in \ideal \OO(X)$, 
  define the \emph{vanishing of $I$}, $V(I) \in \SUB\M\SET(X)$, by 
  \[
    A \in \M\op \mapsto \set{\ph \in \AFF(\SP A, X) \st 
    I \subs \ker \ph^\flat}
  \] 
  In particular, for $I = (f)$,
  we write $V(f)$ instead of $V((f))$.
  A subfunctor $Z$ of $X$ is called \emph{closed} when 
  there exists $I \in \ideal \OO(X)$ such that $Z = V(I)$.
\end{dfn}
\begin{prop}[Basic Facts about Closed Subfunctors]
  
  Let $X \in \AFF$.
  Then the following are true : 
  \begin{itemize}
    \item (Closed Subfunctors are Affine) 
    For $I \in \ideal\OO(X)$,
    $V(I)$ is representable by $\OO(X)/I$ and
    $I = \ker \brkt{\OO(X) \to \OO(V(I))}$.
    Hence for any closed subfunctor $Z$ of $X$,
    $Z$ is an affine scheme and 
    $Z = V(I(Z))$ where $I(Z) := \ker \brkt{\OO(X) \to \OO(Z)}$
    is called the \emph{ideal of definition of $Z$}.

    \item (Ideals, Vanishing Adjunction)
    For $I, J \in \ideal \OO(X)$,
    $I \subs J$ if and only if $V(J) \subs V(I)$.

    \item (Arbitrary Intersection of Closed)
    Let $\XX$ be a collection of closed subfunctors of $X$.
    Then $\bigcap_{Z \in \XX} Z = V(\dsum{Z \in \XX}{} I(Z))$.
    
    \item (Base Change / ``Preimage of Closed are Closed'')
    Let $\ph \in \AFF(Y,X)$, $I \in \ideal \OO(X)$.
    Let the following be a pullback diagram : 
    \begin{cd}
      Y \ar[r,"\ph"] & X \\
      \ph\inv V(I) \ar[u] \ar[r] & V(I) \ar[u]
    \end{cd}
    Then $\ph\inv V(I) = V(\OO(Y)\ph^\flat I)$.
    % \item (Fiber Product)
    % Let $X,X_1 \in \AFF/Y$ where $Y \in \AFF$.
    % Let $I,I_1$ be ideals of $\OO(X)$, $\OO(X_1)$ respectively. 
    % Then we have the pullback diagram : 
    % \begin{cd}
    %   V(I) \ar[r] & Y \\
    %   V(I \otimes_{\OO(Y)} \OO(X_1) + \OO(X) \otimes_{\OO(Y)} I_1) 
    %   \ar[u] \ar[r] & V(I_1) \ar[u]
    % \end{cd} 
    % \item (Composition of Closed Immersions)
    % For a morphism $\ph \in \AFF(Y,X)$,
    % call $\ph$ a \emph{closed immersion}
    % when 
  \end{itemize}
\end{prop}

\begin{prop}[Open Subfunctors of Affine Schemes]
  
  Let $X \in \AFF$. Then the following are true : 
  \begin{itemize}
    \item (Open Subfunctors) For $I \in \ideal\OO(X)$,
    the following two subfunctors of $X$ are equal : 
    \begin{itemize}
      \item (``Complement of $V(I)$'')
      Define $X\minus V(I)$ by setting 
      $\brkt{X\minus V(I)}(A)$ to be 
      the set of $\al \in \AFF(\SP A, X)$ such that
      $\al\inv V(I) = \SP 0$, the ``empty affine scheme''.
      \item (``Support of $I$'')
      Define $D(I)$ by setting 
      $D(I)(A)$ to be the set of $\al \in \AFF(\SP A, X)$ such that 
      $A = A\al^\flat I$.
    \end{itemize}
    A subfunctor $U$ of $X$ is called \emph{open} when 
    there exists $I \in\ideal\OO(X)$ such that $U = D(I) = X\minus V(I)$.

    We will use $\open X$ to denote the full subcategory of $\SUB\M\SET(X)$
    consisting of open subfunctors of $X$.
    % \item (Multiplicative Group Scheme and Basic Opens)
    % Consider the functor $\G^\times \in \M\SET$ defined by 
    % $A \in \M\op \mapsto A^\times$.
    % Then \begin{itemize}
    %   \item $\G^\times = D(\id{\A^1}) = \A^1\minus V(\id{\A^1})$ 
    %   as subfunctors of $\A^1$.
    %   \item $\G^\times$ is representable by $\Z[T,T\inv]\op$ and hence affine.
    %   \item For any $f \in \OO(X)$,
    %   define 
    % \end{itemize}
    \item (Ideal, Open Adjunction)
    Let $I, J \in \ideal\OO(X)$.
    Then $D(I) \subs D(J)$ if and only if $\sqrt{I} \subs \sqrt{J}$.
    In particular, for $U \in \open X$,
    there exists a unique $I_U \in \ideal\OO(X)$ such that 
    $\sqrt{I_U} = I_U$ and $U = D(I_U)$.

    \item (``Fields given enough points for Opens'')
    For any $Y \in \M\SET$, 
    define $Y^\pts$ to the restriction of $Y$ to 
    the full subcategory $\pts$ of $\M\op$ consisting of 
    $K\op$ where $K$ is a field. 
    We will call $Y^\pts$ the \emph{points of $Y$}.

    Then for $U, V$ opens of $X$,
    $U = V$ if and only if $U^\pts = V^\pts$.
    \item 
    For $\UU \subs \open X$,
    define the \emph{open union of $\UU$} to be \[
      \obigcup_{U \in \UU} U := X\minus \bigcap_{U \in \UU} V(I_U)
      = D\brkt{\dsum{U \in \UU}{} I_U}
    \]
    Then for $\UU \subs \open X$, 
    \begin{itemize}
      \item (Choice)
      for any $\set{J_U}_{U \in \UU} \subs \ideal\OO(X)$ where 
      each $U = D(J_U)$, 
      we have $\obigcup_{U \in \UU} U = D(\dsum{U \in \UU}{} J_U)$.
      \item (``Open Cover'') TFAE : 
      \begin{enumerate}
        \item (Intuitive) $\obigcup_{U \in \UU} U = X$.
        \item (Partition of Unity) $\OO(X) = \dsum{U \in \UU}{} J_U$
        where $\set{J_U}_{U \in \UU}$ is any collection of ideals of $\OO(X)$
        such that $U = D(J_U)$ for each $U$.
        \item (Surjective on Points) 
        For all $x : \SP K \to X$ where $K$ is a field, 
        there exists $U \in \UU$ such that $x$ factors through $U$.
      \end{enumerate}
      We say $\UU$ \emph{covers} $X$ when 
      any (and thus all) of the above are true. 
    \end{itemize}

    \item (Base Change / ``Preimage of Opens are Open'')
    Let $\ph \in \AFF(Y,X)$, $I \in \ideal \OO(X)$.
    Let the following be a pullback diagram : 
    \begin{cd}
      Y \ar[r,"\ph"] & X \\
      \ph\inv D(I) \ar[u] \ar[r] & D(I) \ar[u]
    \end{cd}
    Then $\ph\inv D(I) = D(\ph^\flat I)$.
    Hence the pullback of opens along morphisms of affine schemes 
    remain open.

    \item (Fiber Product)
    Let $X,X_1 \in \AFF/Y$ where $Y \in \AFF$.
    Let $I,I_1$ be ideals of $\OO(X)$, $\OO(X_1)$ respectively. 
    Then we have the pullback diagram : 
    \begin{cd}
      D(I) \ar[r] & Y \\
      D(I \otimes_{\OO(Y)} I_1) \ar[u] \ar[r] & D(I_1) \ar[u]
    \end{cd} 
    In particular, $X = X_1 = Y$ implies 
    the intersection of two opens of $X$ is an open of $X$.
  \end{itemize}
\end{prop}
\begin{proof}~

  \textit{(Open Subfunctors)}
  $A \otimes_{\OO(X)} \OO(X)/I = A/A\al^\flat I$.

  \textit{(Ideal, Open Adjunction)}
  The reverse is straightforward. 
  For forward implication, it suffices that $I \subs \sqrt{J}$.
  Suppose we have $f \in I \minus \sqrt{J}$,
  in particular $\OO(X) \neq 0$.
  Consider $\io : \SP (\OO(X)/J)_f \to X$.
  Then $\io \in D(I) \minus D(J)$ since 
  $(\OO(X)/J)_f$ a non-zero ring by assumption.
  This is a contradiction. 

  \textit{(Fields give enough points for opens)}
  Forwards is clear. Let $U = D(I), V = D(J)$.
  For reverse, suppose $D(I) \neq D(J)$.
  WLOG let $\al \in D(I)(A) \minus D(J)(A)$.
  We're looking for a ``point'' 
  $\SP K \to D(I)$ that doesn't lift to $D(J)$.
  Well, since $A\al^\flat J \ssubs A$, by Zorn's lemma 
  there exists a map $\ev_x : A \to K$ where $K$ is a field and 
  $J \subs \ker\ev_x$.
  Then $\al \circ x \in D(I)(K) \minus D(J)(K)$ as desired.

  \textit{(Choice)}
  Straightforward by checking on points. 
  \textit{(Open Cover, Base Change, Fiber product)}
  Straightforward.

\end{proof}

\begin{dfn}[Open Subfunctors, Open Covers]
  
  Let $X \in \M\SET$.
  For $U \in \SUB\M\SET(X)$,
  $U$ is called \emph{open} when 
  for all $\al : \SP A \to X$, the pullback $\al\inv U$ of $U$ along $\al$
  is an open of $\SP A$.
  \begin{cd}
    \SP A \ar[r,"\al"] & X \\
    \al\inv U \ar[u] \ar[r] & U \ar[u]
  \end{cd}
  We will use $\open X$ to denote the 
  full subcategory of $\SUB\M\SET(X)$ consisting of opens.
  When $X$ is affine, 
  this agrees with our specialized notion for affine schemes.
\end{dfn}

\begin{prop}[Basic Facts about Open Subfunctors]
  
  The following are true : \begin{itemize}
    \item (``Extensionality'')
    Let $U, V \in \open X$.
    Then $U = V$ if and only if $U^\pts = V^\pts$.
    \item (Composition)
    Let $V \in \open U$, $U \in \open X$, $X \in \M\SET$.
    Then $V \in \open X$.
    \item (Base Change/``Preimage of Opens are Opens'') 
    Let $X \in \M\SET$, $U \in \open X$ and $\ph \in \M\SET(Y,X)$.
    Then the pullback $\ph\inv U$ of $U$ along $\ph$ is 
    an open of $Y$.
    \begin{cd}
      Y \ar[r,"\ph"] & X \\
      \ph\inv U \ar[u] \ar[r] & U \ar[u]
    \end{cd}
    \item (Fiber Product)
    Let $U,U_1$ be opens of $X,X_1 \in \M\SET$ respectively.
    Then for any $X \to S, X_1 \to S$, 
    the fiber product $U \times_S U_1$ is an open of $X \times_S X_1$.
    In particular, for $X = X_1 = S$,
    this proves the intersection of two opens of $X$ is 
    again an open of $X$.
    \item (``Open Cover'')
    Let $\UU \subs \open X$. TFAE : 
    \begin{itemize}
      \item (``Looks like Open Cover when Tested'') 
      For all $(A,\al) \in \SP\darrow X$,
      $\obigcup_{U \in \UU} \al\inv U = \SP A$. 
      \item (``Surjective on Points'')
      For all $x : \SP K \to X$ where $K$ is a field, 
      there exists $U \in \UU$ such that $x$ factors through $U$.
    \end{itemize}
    We say $\UU$ \emph{covers} $X$ when 
    any (and thus all) of the above are true. 
    \item (Base Change of Open Cover)
    Let $\ph \in \M\SET(Y,X)$ and $\UU \subs \open X$ cover $X$.
    Then $\ph\inv U := \set{\ph\inv U}_{U \in \UU}$ covers $Y$.
  \end{itemize}
\end{prop}
\begin{proof}
  (Extensionality) $U = V$ if and only if 
  for all $\al : \SP A \to X$, 
  $\al\inv U = \SP A$ if and only if $\al\inv V = \SP A$. 
  This reduces to the affine global case.
\end{proof}

\end{document}